---
title: "Part 1 binary Logistic Regression"
author: "Iris Foxfoot"
date: "1/23/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(broom)
library(GGally)
library(palmerpenguins)
library(jtools)
```

```{r}
penguins %>% 
  select(species, bill_length_mm:sex) %>% 
  ggpairs(aes(color = species))
```

Create a subset with only Adelie and Chinstraps
```{r}
adelie_chinstrap <- penguins %>% 
  filter(species %in% c("Adelie", "Chinstrap")) %>% 
  mutate(species = fct_drop(species)) #drops gentoos factor
```

Lets just dataviz of these two species:
```{r}
ggplot(data = adelie_chinstrap, aes(x = body_mass_g, y = flipper_length_mm)) + geom_point(aes(color = sex)) + facet_wrap(~ species)
```

Binary Logistic Regression



-body mass
-flipper length
-penguin sex

```{r}
adelie_chinstrap_blr <- glm(species ~ body_mass_g + flipper_length_mm + sex, 
                            data = adelie_chinstrap, 
                            family = "binomial")
```

Take a look at the outcomes: 
```{r}
adelie_chinstrap_blr

summary(adelie_chinstrap_blr)
```

```{r}
ggplot(data = adelie_chinstrap, aes(x = species, y = flipper_length_mm)) + geom_jitter(aes(color = sex))
```

What are the actual prob of being chinstrap for each of the existing observations in our adelie_chinstrap data frame
```{r}
blr_fitted <- adelie_chinstrap_blr %>% 
  broom::augment(type.predict = "response")

```

Plotting fitted probabilities
```{r}
ggplot(data = blr_fitted, aes (x = flipper_length_mm, y = .fitted)) + geom_point(aes(color = sex, pch = species)) + geom_smooth(aes(color = sex, se = FALSE)) + labs(x = "flipper length (mm)", y = " Probability of outcomes Chinstrap")

```

Quick overview of model based on different variables
```{r}
effect_plot(adelie_chinstrap_blr,
            pred = flipper_length_mm,
            y.label = "Probability of Chinstrap", 
            interval = TRUE)

effect_plot(adelie_chinstrap_blr,
            pred = body_mass_g,
            y.label = "Probability of Chinstrap", 
            interval = TRUE)

```

What is the prob that a female penguin weighing 3410 g with a flipper length of 192mm is a chinstrap?

```{r}
ex_1 <- predict(adelie_chinstrap_blr,
                data.frame(sex = "female", 
                           body_mass_g = 3410,
                           flipper_length_mm = 192), 
                type = "response")
ex_1
```

